Creating a fluid process for understanding multi-dimensional data/simulations is a difficult task. The Media Arts and Technology program at UCSB focuses on lending artistics practices in constructing visualizations of scientic data. These often depict comlex concepts such as quantum mechanics, MRI data, etc. using openGL algorithms to create visual representations. Similarly, Gamma--a powerful computer synthesis library-- is used to create auditory representations using purely mathematically-generated waveforms.

\iffalse
@@@ TODO: Fill in this file with references to Allopshere related research,
and then rename it allosphere.tex

And make main.tex include it, and change the section title etc.

Wright, Matthew and Edgar Berdahl. 2006. “Towards Machine Learning of Expressive Microtiming in Brazilian Drumming.” \cite{Wright2006BrazDrumML}

Write a paragraph or two about that here.





Here is an example of a related work section and how to cite sources.

The benefits of SBL have been most explored in introductory
courses \cite{p55-gestwicki, p505-hendrix, p165-narayanan}, but have
also been applied to specialized topics, including Human Computer
Interaction \cite{p117-hundhausen} and Game Design
\cite{p64-estey}. Game design and HCI require a hybrid mastery of
artistic elements and programming abilities. The artistic qualities of
these disciplines naturally lend themselves to the benefits of SBL,
which has a long history in the arts.

Participation in courses featuring SBL has shown to give students a
greater confidence in their own project quality and programming
abilities, and creates a sense of community among CS
students~\cite{p887-bergin, p64-estey}. As a part of SBL, students are
given the opportunity to enhance and exhibit skills that may be
neglected in a traditional computer science education---students often
collaborate as a team, discuss competing solutions, and explain their
work to their peers~\cite{p505-hendrix}.  Working collectively not
only creates an environment where students can learn from each
other---increasing their technical skills, but they also gain valuable
communication skills~\cite{p165-narayanan}. SBL is a well-attuned
educational response to industry desires for more refined
interpersonal and team skills from Computer Science
graduates~\cite{p64-estey}.  While the application of SBL to CS is
still in its early stages, and has yet to be widely adopted, the
studies that have been done have shown promising results.
\fi
